\documentclass[dvips,12pt]{article}


\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{lipsum} % for filler text
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhead{} % clear all header fields
\fancyhead[LE,RO]{Project Proposal}
\fancyhead[RE,LO]{Team A}
\renewcommand{\headrulewidth}{0pt} % no line in header area
\fancyfoot{} % clear all footer fields
\fancyfoot[LE,RO]{\thepage}           % page number in "outer" position of footer line
\fancyfoot[RE,LO]{}

\setlength{\oddsidemargin}{0.25in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{0in}
\setlength{\textheight}{8.5in}


\begin{document}
\title{\textbf{Project Stack}\\ \small{}Sharing Knowledge Is Power}
\author{\textbf{Team A}\\A1: Noymul Islam Chowdhury 2012331034\\A2: Asif Mohaimen 2012331054\\\\
\textbf{Team B}\\Quazi Ishtiaque Mahmud 2012331051\\Nowshad Hasan 2012331052}
\maketitle

\begin{center}
\underline{Submitted by}

Team A
\end{center}
\clearpage

\section{Aims}
Archiving project and research works of students \& teachers of different  universities  of Bangladesh and also provide project \& personal profile analyzing service for different personnel from different universities in Bangladesh and connecting them with the software industries.

\section{Objectives}
\begin{itemize}
\item We will collect data about project and research works of all the teachers and students.
\item The key thing will be the review system for each and every project. We will build an automated system using machine learning algorithms which will determine the project strength by the reviews from the project organizer \& other people who will be seeing it online.
\item When the project will be uploaded the user will have to provide a precise description of the project and we shall use the project review to determine his profile strength also by using machine learning algorithms. So these will be our key objectives for this project.
\item Different universities can connect to our network and can use our services with  yearly payments and individuals can update their account to premium account to use privileged services like- \emph{highlights, boosting etc}. 
\end{itemize}

\section{Importance}

As we do not have any access to the previous works done by the students and teachers of  different departments of different universities, this service will help us to have easy access to the works done by the people of different universities. Sometimes we might get puzzled if it is a literal good work to review and might get disappointed after watching the whole project. The review system will resolve the problem and predict if it should be broken down deep inside or not. So this complete project will be saving the time of the reviewer.
\clearpage
\section{Working Plan for Minimum Viable Product}

\begin{itemize}
\item Literature search and review.
\item Analysis and modeling.
\item System design, coding small test programs and simple prototypes.
\item System implementation.
\item System testing \& evaluation.
\item Work on final Report.
\end{itemize}

\end{document}